\section{ARLib}\label{arlib}

This is the main library we are developing here. It is comprised of the
following modules:

\begin{itemize}
\item
  \hyperref[sec:video_library]{ARLibVideo}:
  The stereo video input library. It grabs real-time video streams from
  the two cameras\cite{c310} attached to the Oculus Rift DK2\cite{dk2} and provides
  coordinate lookup tables to undistort them according to their lens
  parameters and align them to one another according to their
  precalculated homographies.
\item
  \hyperref[sec:oculus_library]{ARLibOculus}:
  A small wrapper for LibOVR\cite{dk2}. Only the needed parts. It initializes the
  HMD, provides the LibOVR configuration parameters and the latest
  LibOVR tracking data.
\item
  \hyperref[sec:tracking_library]{ARLibTracking}:
  The rigid body tracking library. It uses the NatNetSDK\cite{optitrack} and/or
  ARLibOculus to provide the latest positions and orientations of rigid
  bodies as well as a fraction of their tracking history for retroactive
  queries.
\item
  \hyperref[sec:ogre_library]{ARLibOgre}:
  The OGRE 1.9\cite{ogre} interface library. This is the only part of ARLib that depends on
  OGRE. It provides all the shaders, materials, render targets and
  abstracted components that can be directly inserted into a scene.
\end{itemize}

\section{ARLib\_Samples}\label{arlibux5fsamples}

We provide two simple example projects that demonstrate the usage of
ARLib within OGRE:

\begin{itemize}
\item
  \hyperref[sec:simple_scene]{SimpleScene}:
  A simple example scene with some static objects placed around the
  origin.
\item
  \hyperref[sec:remote_game]{RemoteGame}:
  A simple game where one has to defend against laser bullets of a \emph{Star
  Wars Remote}.
\end{itemize}