\begin{center}
\textbf{Developed by Andreas Mantler}
\end{center}
ARLibOculus is just a lightweight single-class wrapper for the needed parts of LibOVR (the Oculus SDK)\cite{dk2}.
Including \href{https://github.com/ands/OculusMeetsAR/blob/master/ARLib/include/ARLib/Oculus/Rift.h}{ARLib/Oculus/Rift.h} won't pull any LibOVR header files into the compilation unit.
In fact, it doesn't depend on anything at all!

\section{\texorpdfstring{\href{https://github.com/ands/OculusMeetsAR/blob/master/ARLib/include/ARLib/Oculus/Rift.h}{ARLib::Rift}}{ARLib::Rift}}\label{arlibrift}
\texttt{ARLib::Rift} has some static methods as well as non-static ones.
The static methods are needed to initialize and shutdown the LibOVR system as a whole,
while the non-static methods operate on single instances of Oculus Rift devices.

\subsubsection{Static Methods}\label{static-methods}

\begin{lstlisting}
static void init();
\end{lstlisting}
Initializes LibOVR. Must be called once before using anything else from ARLibOculus.

\begin{lstlisting}
static void shutdown();
\end{lstlisting}
Shuts down LibOVR. Should be called once after deleting all \texttt{ARLib::Rift} instances.

\begin{lstlisting}
static bool available(int id);
\end{lstlisting}
Test if an Oculus Rift device with the specified id is connected (0 is the first connected Rift).

\subsubsection{Methods}\label{methods}

\begin{lstlisting}
enum RIFT_ERROR_CODE
{
    RIFT_OK,
    RIFT_CONNECTION_ERROR,
    RIFT_TRACKING_ERROR
};

RIFT_ERROR_CODE initialize(int id);
\end{lstlisting}
Initializes the instance. Tries to connect to the Oculus Rift device with the specified id. Returns \texttt{RIFT\_OK} on success.

\begin{lstlisting}
void getTextureSizes(
    int *size2dL,
    int *size2dR);
\end{lstlisting}
Writes the recommended render target texture/framebuffer resolutions for each eye into the specified \texttt{int{[}2{]}} arrays.

\begin{lstlisting}
void getUVScalesAndOffsets(
    float *scale2dL, float *offset2dL,
    float *scale2dR, float *offset2dR);
\end{lstlisting}
Writes texture coordinate shader parameters for each eye to the specified \texttt{float{[}2{]}} arrays.
These have to be passed as uniforms to the \href{https://github.com/ands/OculusMeetsAR/blob/master/ARLib/ogre_media/ARLibOculusDistortionVertex.glsl}{ARLibOculusDistortionVertex.glsl} shader.

\begin{lstlisting}
struct DistortionVertex
{
    // [-1,+1],[-1,+1] over the entire framebuffer:
    float ScreenPosNDC[2];

    // Lerp factor between time-warp matrices. Can be encoded in Pos.z:
    float TimeWarpFactor; 

    // Vignette fade factor. Can be encoded in Pos.w:
    float VignetteFactor;

    // Chromatic aberration correction parameters:
    float TanEyeAnglesR[2];
    float TanEyeAnglesG[2];
    float TanEyeAnglesB[2];
};

void getDistortionGeometries(
    DistortionVertex **verticesL, int *vertexNumL,
    unsigned short **indicesL, int *indexNumL,
    DistortionVertex **verticesR, int *vertexNumR,
    unsigned short **indicesR, int *indexNumR);
\end{lstlisting}
Writes pointers to triangle mesh data and data quantities for the distortion meshes of each eye to the specified locations.

\begin{lstlisting}
void getProjections(
    float znear, float zfar, bool rightHanded,
    float *aspectRatioL, float *projection4x4L,
    float *aspectRatioR, float *projection4x4R);
\end{lstlisting}
For specified near and far distances, writes device aspect ratios and projection matrices for each eye into the specified locations.

\begin{lstlisting}
void getPose(float *position3d, float *orientationQuaternionXYZW);
\end{lstlisting}
Writes the latest LibOVR tracking position and orientation to the specified \texttt{float{[}3{]}} and \texttt{float{[}4{]}} arrays.

\begin{lstlisting}
void recenterPose();
\end{lstlisting}
Will recenter the tracking position and orientation (yaw component) to the current pose.

\begin{lstlisting}
float getInterpupillaryDistance();
\end{lstlisting}
Returns the configured IPD (interpupillary distance) for the current LibOVR user.

\begin{lstlisting}
bool isPositionCurrentlyTracked();
bool isOrientationCurrentlyTracked();
bool isCameraPoseCurrentlyTracked();
bool isPositionTrackingConnected();
\end{lstlisting}
Various LibOVR tracking state flags.